\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-06 tex/paper.tex
Updated the equations

\end{description}
\newpage
\section{Model} \label{sec:model}
The model for this work shows how the data can only be accessed or modified by authorized
users and how the defined integrity of the data is always kept in the Perius system.

@@

In this section the consequences of different operations are stated in an informal mathematical
manner. These rules are what should be expected to be followed by the implementation in
Section~\ref{sec:implementation}.

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(o)            & User u reads object o\\ \hline
        u, write(o)           & User u writes object o\\ \hline
        u, copy(o)            & User u copies object o and the copy gets a new ID\\ \hline
        u, change(o)          & User u locally changes object o \\ \hline
        u, modify(o', o)      & User u globally modifies object o based on object o'\\ \hline
        u, delete(o)          & User u deletes object o\\ \hline
        u, snapshot(o)        & User u takes a snapshot of object o \\ \hline
    \end{tabular}
\end{center}

\begin{equation} \label{eq:fileupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        f  & = f \in m' \land \\
        f' & = u, change(f) \land \\
        u, & write(f') \land \\
        u, & modify(f', m) \Implies f \in F \land f' \in F
    \end{split}
\end{equation}
\begin{equation}
    \begin{split}
        (F, f \in c) \xrightarrow{update(f', c)} (\{f, f'\} \subset F, f' \in c) 
    \end{split}
\end{equation}
\inferrule
{f \in c \xrightarrow{update(f', c)} f' \in c }
{c \cap \{f\} \\ c \cup \{f'\} \\ F \cup \{f, f'\}}

\vspace{2em}

\inferrule
{f \in c \\ update(f', c) \\ f' \in c}
{F \cup \{f, f'\}}

\vspace{2em}

\inferrule
{f \in F \\ [fileId = f.id, \dots] \in C \\ f \neq f'} 
{F \cup \{f\} \xrightarrow{write(fileId, f'.id)} F \cup \{f, f'\}}

\vspace{2em}
If a user wants to update a file in a content, the file is copied and the original is intact.

\begin{equation} \label{eq:contentupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        m'' & = u, change(m') \land \\
        m''' & = u, modify(m'', m) \Implies \\
        m''' & \in M \land m \not \in M
    \end{split}
\end{equation}
If a user reads content and then writes to it, the content is directly changed.

\begin{equation} \label{eq:containerupdate}
    \begin{split}
        c' & = u, read(c) \land \\
        c'' & = u, change(c') \land \\
        c''' & = u, modify(c'', c) \Implies \\
        c''' & \in C \land c \not \in C
    \end{split}
\end{equation}
If a user reads a container and then writes to it, the container is directly changed.

\begin{equation} \label{eq:copy}
    \begin{split}
        & f' = f \in m \\
        & m' = u, copy(m) \Implies \\
        & m' \neq m \land \\
        & f' \in m' \land f' \in m
    \end{split}
\end{equation}
If a user copies a content, the new content is not equal to the old (because of its new ID), however
they both refer to the same file.

\begin{equation} \label{eq:snapshot}
    \begin{split}
        s = u, snapshot(c') \Implies \\
        \forall c \in c', u, copy(c) \in s \land \\
        \forall m \in c', u, copy(m) \in s \land \\
        (\forall f \in c' \Implies f \in s)
    \end{split}
\end{equation}
If a user creates a snapshot of a container the full container tree is re-created with new IDs and
its content still refers to the same files.

\begin{equation} \label{eq:delete}
    \begin{split}
        f' = f \in (u, read(c)),  \\
        u, delete(c) \Implies \\
        c \not \in C \land f' \in F
    \end{split}
\end{equation}
If a user deletes content, the file referred to in the content is not deleted.

@@

\hfill \\
\textbf{REST Endpoints} \hfill \\
For the front-end to communicate with the back-end, a RESTful service is implemented.
The following endpoints were configured:

>>>>

\end{description}
\newpage
\section{Model} \label{sec:model}
This section describes how different operations can be expected to effect the data in the system.
The model for this work also shows how the data can only be accessed or modified by
authorized users and how the defined integrity of the data is always kept in the Perius system.

@@

In this section the consequences, side effects and direct effects, of different operations are
stated in an informal mathematical manner, similar to how inference rules are composed. These rules
are what should be expected to be followed by the implementation in
Section~\ref{sec:implementation}.

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(o)            & User u reads object o\\ \hline
        u, write(o)           & User u writes object o\\ \hline
        u, copy(o)            & User u copies object o and the copy gets a new ID\\ \hline
        %u, change(o)          & User u locally changes object o \\ \hline
        u, update(o, o')      & User u globally modifies object o based on object o'\\ \hline
        %u, modify(o', o)      & User u globally modifies object o based on object o'\\ \hline
        u, delete(o)          & User u deletes object o\\ \hline
        u, snapshot(o)        & User u takes a snapshot of object o \\ \hline
    \end{tabular}
\end{center}

To describe a content object \textit{m} containing fileId \textit{f}, the following syntax is used:
$[fileId = f.id, \dots] \in M$, the same syntax is also applied to different types of objects
throughout the explanation of the model.

%\begin{equation} \label{eq:fileupdate}
%    \begin{split}
%        m' & = u, read(m) \land \\
%        f  & = f \in m' \land \\
%        f' & = u, change(f) \land \\
%        u, & write(f') \land \\
%        u, & modify(f', m) \Implies f \in F \land f' \in F
%    \end{split}
%\end{equation}
%\begin{equation}
%    \begin{split}
%        (F, f \in c) \xrightarrow{update(f', c)} (\{f, f'\} \subset F, f' \in c) 
%    \end{split}
%\end{equation}

\vspace{2em}
\textbf{File Update}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {f \in F \\ [fileId = f.id, parent = c \dots] \in M \\ A[u,c] \in A} 
    {F \cup \{f\} \xrightarrow{u, update(fileId, f'.id)} F \cup \{f, f'\}}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to a parent container \textit{c} of content \textit{m},
updates a file reference \textit{f} in content \textit{m}, the original file stays intact.

%\begin{equation} \label{eq:contentupdate}
%    \begin{split}
%        m' & = u, read(m) \land \\
%        m'' & = u, change(m') \land \\
%        m''' & = u, modify(m'', m) \Implies \\
%        m''' & \in M \land m \not \in M
%    \end{split}
%\end{equation}

\vspace{2em}
\textbf{Content Update}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {m \in M \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \xrightarrow{u, update(m, m')} M \cup \{m'\}}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to a parent container \textit{c} of content \textit{m}
updates that content, the content is directly changed, without any Copy-on-Write.

%\begin{equation} \label{eq:containerupdate}
%    \begin{split}
%        c' & = u, read(c) \land \\
%        c'' & = u, change(c') \land \\
%        c''' & = u, modify(c'', c) \Implies \\
%        c''' & \in C \land c \not \in C
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Container Update}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {c \in C \\ A[u,c] \in A}
    {C \cup \{c\} \xrightarrow{u, update(c, c')} C \cup \{m'\}}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to a container \textit{c} updates that container, the
container is directly changed, without any Copy-on-Write.

%\begin{equation} \label{eq:copy}
%    \begin{split}
%        & f' = f \in m \\
%        & m' = u, copy(m) \Implies \\
%        & m' \neq m \land \\
%        & f' \in m' \land f' \in m
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Copy}
\begin{equation} \label{eq:copy}
    \inferrule
    {m \in M \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \xrightarrow{u, copy(m')} M \cup \{m, m'\} \land m.id \neq m'}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to the parent (source and destination) container \textit{c}
of content \textit{m} copies that content, the new content \textit{m'} is not equal to the old
(because of its new ID), however they both contain the same metadata and refer to the same file.

\vspace{2em}
\textbf{Delete}
\begin{equation} \label{eq:delete}
    \inferrule
    {m \in M \\ f \in F \\ f \in m \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \land F \cup \{f\} \xrightarrow{u, delete(m)} M \cup \{\} \land F \cup \{f\}}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to a parent container \textit{c} of content \textit{m}
deletes that content, the file \textit{f} referred to in the content is not deleted.

\vspace{2em}
\textbf{Snapshot}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        [C', M'] = u, snapshot(tree) \Implies \\
        \forall c \in tree, u, copy(c) \in C \land \\
        \forall m \in tree, u, copy(m) \in M \land \\
        (\forall f \in tree \Implies f \in F)
    \end{split}
\end{equation}

To explain the non-trivial snapshot operation it is first defined in \ref{eq:snapshot}. The snapshot
operation is performed upon a tree of objects and results in two new sets (C' and M'), one with
containers and one with content, the referred files remain the same as before the snapshot.

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {c \in C \\ A[u,c] \in A}
    {M \land C \xrightarrow{[C', M'] = u, snapshot(c)} M \cup M' \land C \cup C'}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

%\begin{equation} \label{eq:delete}
%    \begin{split}
%        f' = f \in (u, read(c)),  \\
%        u, delete(c) \Implies \\
%        c \not \in C \land f' \in F
%    \end{split}
%\end{equation}

@@

\hfill \\
\textbf{REST Endpoints} \label{sec:API} \hfill \\
For the front-end to communicate with the back-end, a RESTful service is implemented.
The following endpoints were configured:
